---
title: "Figure2"
author: "Dario Righelli"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
```{r,eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("SingleCellMultiModal")
```


```{r}
library(SingleCellMultiModal)
library(UpSetR)
```

# Retrieving data

```{r}
(mae <- CITEseq(DataType="peripheral_blood", modes="*", dry.run=FALSE, version="1.0.0"))
```

# Plotting Upset 

The upset plot represents the numerosity insersections across the modalities
in terms of samples.

## All conditions

We are now plotting an upset showing the total number of samples in our 
`MultyAssayExperiment` object and how they are distributed across the three 
modalities.

```{r}
upsetSamples(mae, text.scale=c(2,2,2))
```

## CTCL condition

To better understand the distribution of the samples across the modalities we
split them based on the experimental conditions.

Here we plot the cutaneous T-cell lymphoma (CTCL) samples.

```{r}
(ctclMae <- mae[,colData(mae)$condition == "CTCL",])
upsetSamples(ctclMae, text.scale=c(2,2,2))
```

Here we plot the control (CTRL) samples.

```{r}
(ctrlMae <- mae[,colData(mae)$condition == "CTRL",])
upsetSamples(ctrlMae, text.scale=c(2,2,2))
```

# SessionInfo 

```{r, tidy=TRUE}
sessionInfo()
```





